Surrogate model for an aligned-spin effective one body waveform model of binary neutron star inspirals using Gaussian process regression

### 2019-05-14 paper/paper.tex
Changed AEI address.
Load utf8 package
Address item 3

@@

\author{
Benjamin D. Lackey, 
Michael P\"{u}rrer, 
Andrea Taracchini,
Sylvain Marsat
}
\affiliation{
Max Planck Institute for Gravitational Physics, Albert Einstein Institute, D-14476 Golm, Germany
}

@@

The EOB approach to the general-relativistic 2-body problem, first described in Ref.~\cite{Buonanno:1998gg}, has proven successful in modeling the dynamics and GW emission of compact binaries. State-of-the-art aligned-spin EOB models~\cite{Bohe:2016gbl,Nagar:2017jdw} can accurately match hundreds of NR simulations of aligned-spin BBH systems for mass ratios up to 8 and spin magnitudes up to 0.85 for unequal-mass (up to 0.98 for equal-mass) binaries. The EOB framework can also accommodate precessing-spin BBHs, showing good agreement to mildly precessing NR simulations~\cite{Babak:2016tgq}.

>>>>

%%% contains utf-8, see: http://inspirehep.net/info/faq/general#utf8
\usepackage[utf8]{inputenc}

@@

\author{
Benjamin D. Lackey, 
Michael P\"{u}rrer, 
Andrea Taracchini,
Sylvain Marsat
}
\affiliation{
%Max Planck Institute for Gravitational Physics, Albert Einstein Institute, D-14476 Golm, Germany
Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam-Golm 14476, Germany
}

@@

The EOB approach to the general-relativistic 2-body problem, first described in Ref.~\cite{Buonanno:1998gg}, has proven successful in modeling the dynamics and GW emission of compact binaries. State-of-the-art aligned-spin EOB models~\cite{Bohe:2016gbl,Nagar:2017jdw} can accurately match hundreds of NR simulations of aligned-spin BBH systems for mass ratios up to 8 and spin magnitudes up to 0.85 for unequal-mass (up to 0.994 for equal-mass) binaries. The EOB framework can also accommodate precessing-spin BBHs, showing good agreement to mildly precessing NR simulations~\cite{Babak:2016tgq}.
